---
weight: 5
title: "Host site on GitHub"
author: "Ming Chen"
output: html_document
---

<style>
pre code, pre, code {
  white-space: pre !important;
  overflow-x: scroll !important;
  word-break: keep-all !important;
  word-wrap: initial !important;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Initialize the project as a github repository

`cd` to the project directory and run the command

```{r eval=FALSE}
git init .
git add . 
git commit 'init project'
```

#### Link local repository to an empty remote github repository

```{r eval=FALSE}
git remote add origin https://github.com/MingChen0919/blogdown-website-with-hugo-theme-learn.git
```

#### Host site on github

* render the site with `blogdown::serve_site()`
* copy **public/** to **docs/**: `cp -r public/ docs/`
* push updates to github: `git add . && git commit -m 'updates' && git push`
* change GitHub pages source to **master branch /docs folder**
    + this can be done by go to the github repository, click **settings**, find the **GitHub Pages** section, and then select **master branch /docs folder**.



