---
weight: 2
title: "Host site on GitHub"
author: "Ming Chen"
output: html_document
---

<style>
pre code, pre, code {
  white-space: pre !important;
  overflow-x: scroll !important;
  word-break: keep-all !important;
  word-wrap: initial !important;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Git repository

Go into the project directory and run the command to make the project directory as a git repository.

```{r eval=FALSE}
git init .
git add . 
git commit 'init project'
```

#### Associate git repository with github remote repository

```{r eval=FALSE}
git remote add origin https://github.com/MingChen0919/blogdown-website-with-hugo-theme-learn.git
```

#### The **content/** and `.Rmd` files

All `.Rmd` files should go to the **content/** directory. When running the `blogdown::server_site()` function, the `.Rmd` files within **content/** directory will get rendered and HTML files will be generated and copied to the **publish directory**.

{{% notice note %}}
By default, the **publish directory** is the **public/** directory. However, when hosting a website on GitHub, GitHub can only recognize website files within the **docs/** folder. We need to change the default **publish directory** from **public/** to **docs/**.
{{% /notice %}}

Add the following line to the **config.toml** file to change the default publish directory.

```{r eval=FALSE}
publishDir = "docs"
```


#### Publish site on GitHub

After run the `blogdown::server_site()` function and push all commits to GitHub, go to the github repository, click **settings**, find the **GitHub Pages** section, and then select **master branch /docs folder** and save.



